### 2021-01-20 research project/sections/Introduction.tex
""

The value of $\pi$ has been researched for many years, although under different names,
and the amount of different approaches to reach the value is large.

The value has been found through many processes, be it geometrically, algebraically 
or through other means.

This paper seeks to examine the extent at which two historical methods of
approximation of the value $\pi$, namely the approaches suggested by the aforementioned 
mathematicians Madhava and Viète, differ in terms of computational efficiency and 
speed.

>>>>

The value of $\pi$ has been researched for many years, although under different names,
and the amount of different approaches to reach the value is large. The value has been 
found through many processes, be it geometrically, algebraically 
or through other means.

This paper seeks to examine the extent at which two historical methods of
approximation of the value $\pi$, namely the approaches suggested by the aforementioned 
mathematicians Madhava and Viète, differ in terms of computational efficiency and 
speed, and explain these differences.
